Brief Announcement: A Family of Leaderless Generalized-Consensus Algorithms

### 2016-02-11 podc16/paper2.tex
work on graph linearization, added introductory paragraph

>>>>

The graph processing algorithm must compute $\opn{c-struct}\left( g_p \right)$, as defined below.
Its main property is Lemma 1; Together with Invariants 1 and 2 (TODO, the invariants guaranteed by the dependency-set algorithm and the map-agreement algorithm), Lemma 1 implies that leaderless algorithms safely implement generalized consensus.
